Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-04-25 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd
Modified covariates code to winsorize expression data and removed ribozero and flowcell batch variables

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c('Individual_ID', "Institution", "Gender", "RibozeroBatch", "LibraryBatch", "FlowcellBatch", "Dx.Tissue")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

### Outlier analysis
Detect outlier samples based on their expression (logCPM) pattern
```{r detect.outliers, fig.height=8, fig.width=8, results='asis', cache = FALSE}
indToRemove = c('MSSM_RNA_ACC_BP_24',

                'MSSM_RNA_ACC_375', 'MSSM_RNA_ACC_170', 'MSSM_RNA_ACC_315', 'MSSM_RNA_ACC_250', 'MSSM_RNA_ACC_21', 'MSSM_RNA_ACC_356', 
                'MSSM_RNA_ACC_318', 'MSSM_RNA_ACC_222', 'MSSM_RNA_ACC_220', 'MSSM_RNA_ACC_379', 'MSSM_RNA_PFC_133',

                'MSSM_RNA_PFC_139', 'MSSM_RNA_PFC_163', 'MSSM_RNA_PFC_260', 'MSSM_RNA_PFC_299', 'MSSM_RNA_PFC_361', 'MSSM_RNA_PFC_89', 
                'MSSM_RNA_PFC_319', 'MSSM_RNA_PFC_348', 'MSSM_RNA_PFC_354', 'MSSM_RNA_PFC_60', 'PENN_RNA_PFC_71', 'PENN_RNA_PFC_56')

@@

### Normalisation (with NULL)
Initial normalisation usign cqn and dispersion control with voom (with NULL design)
```{r initial.voom.normalisation, fig.height=5, fig.width=5}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)

# Set gene counts in specific samples that are deviating 3 sd from other samples to 0
log.mat = apply(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)
  return((x < (mn-3*std.dev)) | (x > (mn+3*std.dev)))
}) %>% t
PROCESSED_COUNTS$filteredExprMatrix$counts[log.mat] = 0

# Re-compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
```
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
### Outlier analysis
Clustering of voom adjusted data (with NULL design)
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, scale.=T, center = T)

@@

# Plot abberent distribution of logcpm counts
tmp1 = (CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset) %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  tidyr::gather(SampleID, logCPM, -ensembl_gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID') %>%
              tidyr::separate(Dx.Tissue, c('Dx', 'Tissue'), sep = '_'))

@@

tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

  # Estimate voom weights
  VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix$counts, design=DM1$design, plot=F)
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
  correlation <- parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION, block = COVARIATES$Individual_ID)

@@

  # Fit linear model using new weights and new design
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
  ADJUSTED.FIT = lmFit(VOOM.GENE_EXPRESSION)

  # Residuals after normalisation
  RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(ADJUSTED.FIT, CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset)

@@

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

### Sanity check
```{r residualSigCovars.manual, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              COVARIATES, 
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)

residualSigCovars[["PC_res"]][[2]]$plotData
```
### Residual calculation
Calculate weighted residuals and add back "Dx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("Dx.Tissue", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(RESIDUAL.GENE_EXPRESSION))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION, scale.=T, center = T)

@@

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

# Estimate voom weights
VOOM.WEIGHTS = voom(PROCESSED_COUNTS$filteredExprMatrix$counts, design=DESIGN$design, plot=F)
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
correlation <- parallelDuplicateCorrelation(VOOM.WEIGHTS, block = COVARIATES$Individual_ID)

@@

# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
FIT = lmFit(VOOM.WEIGHTS)

# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.TissueControl_ACC-Dx.TissueOther_ACC",
                                     "Dx.TissueControl_ACC-Dx.TissueSCZ_ACC",
                                     "Dx.TissueOther_ACC-Dx.TissueSCZ_ACC",
                                     "Dx.TissueControl_DLPFC-Dx.TissueOther_DLPFC",
                                     "Dx.TissueControl_DLPFC-Dx.TissueSCZ_DLPFC",
                                     "Dx.TissueOther_DLPFC-Dx.TissueSCZ_DLPFC"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store residual gene expression for network analysis
RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_ACC_DLPFC_netResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for network analysis)', 
                parentId = CODE$properties$id)
annotations(nEXP_OBJ) = annotations(CODE)
annotations(nEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
nEXP_OBJ = synStore(nEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

>>>>

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
#"RibozeroBatch", "FlowcellBatch",
FactorCovariates <- c('Individual_ID', "Institution", "Gender", "LibraryBatch", "Dx.Tissue")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

### Outlier analysis
Detect outlier samples based on their expression (logCPM) pattern
```{r detect.outliers, fig.height=8, fig.width=8, results='asis', cache = FALSE}
indToRemove = c('MSSM_RNA_ACC_BP_24', 'MSSM_RNA_ACC_375', 'MSSM_RNA_ACC_170', 'MSSM_RNA_ACC_315', 'MSSM_RNA_ACC_250',
                'MSSM_RNA_ACC_21', 'MSSM_RNA_ACC_356', 'MSSM_RNA_ACC_318', 'MSSM_RNA_ACC_222', 'MSSM_RNA_ACC_220',
                'MSSM_RNA_ACC_379', 'MSSM_RNA_PFC_133', 'MSSM_RNA_PFC_139', 'MSSM_RNA_PFC_163', 'MSSM_RNA_PFC_260',
                'MSSM_RNA_PFC_299', 'MSSM_RNA_PFC_361', 'MSSM_RNA_PFC_89', 'MSSM_RNA_PFC_319', 'MSSM_RNA_PFC_348',
                'MSSM_RNA_PFC_354', 'MSSM_RNA_PFC_60', 'PENN_RNA_PFC_71', 'PENN_RNA_PFC_56',  "MSSM_RNA_ACC_310",
                "MSSM_RNA_ACC_51",  "MSSM_RNA_ACC_254", "MSSM_RNA_ACC_28", "MSSM_RNA_ACC_293", "MSSM_RNA_ACC_233",
                "MSSM_RNA_ACC_167", "MSSM_RNA_ACC_353", "MSSM_RNA_ACC_355", "MSSM_RNA_ACC_211", "PENN_RNA_ACC_122",
                "PENN_RNA_ACC_049", "PENN_RNA_ACC_052", "PENN_RNA_ACC_068", "PENN_RNA_ACC_070", "PITT_RNA_ACC_10020",
                "PITT_RNA_ACC_1240", "PITT_RNA_ACC_1284", "PITT_RNA_ACC_700", "PITT_RNA_ACC_857", "PITT_RNA_ACC_BP_1589",
                "MSSM_RNA_PFC_230", "MSSM_RNA_PFC_304", "MSSM_RNA_PFC_309", "MSSM_RNA_PFC_329", "MSSM_RNA_PFC_82",
                "PENN_RNA_PFC_5", "PENN_RNA_PFC_58", "PENN_RNA_PFC_99", "PITT_RNA_PFC_1284")

@@

### Normalisation (with NULL)
Initial normalisation usign cqn and dispersion control with voom (with NULL design)
```{r initial.voom.normalisation, fig.height=5, fig.width=5}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E.NA = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset

# Set gene counts in specific samples that are deviating 3 sd from other samples to 0
log.mat = apply(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)
  return((x < (mn-3*std.dev)) | (x > (mn+3*std.dev)))
}) %>% t
PROCESSED_COUNTS$filteredExprMatrix$counts.NA = PROCESSED_COUNTS$filteredExprMatrix$counts
PROCESSED_COUNTS$filteredExprMatrix$counts.NA[log.mat] = NA
PROCESSED_COUNTS$filteredExprMatrix$counts[log.mat] = 0

CQN.GENE_EXPRESSION$E.NA[log.mat] = NA
CQN.GENE_EXPRESSION$E.zero = CQN.GENE_EXPRESSION$E.NA
CQN.GENE_EXPRESSION$E.zero[log.mat] = 0
```
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.zero))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
### Outlier analysis
Clustering of voom adjusted data (with NULL design)
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.zero, scale.=T, center = T)

@@

# Plot abberent distribution of logcpm counts
tmp1 = (CQN.GENE_EXPRESSION$E.NA) %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  tidyr::gather(SampleID, logCPM, -ensembl_gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID') %>%
              tidyr::separate(Dx.Tissue, c('Dx', 'Tissue'), sep = '_'))

@@

tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.zero)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.zero, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

  # Estimate voom weights
  VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix$counts, design=DM1$design, plot=F)
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E.NA
  correlation <- parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION, block = COVARIATES$Individual_ID)

@@

  # Fit linear model using new weights and new design
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E.NA
  ADJUSTED.FIT = lmFit(VOOM.GENE_EXPRESSION)

  # Residuals after normalisation
  RESIDUAL.GENE_EXPRESSION = list()
  RESIDUAL.GENE_EXPRESSION$E.NA = residuals.MArrayLM(ADJUSTED.FIT, CQN.GENE_EXPRESSION$E.NA)
  RESIDUAL.GENE_EXPRESSION$E.zero = RESIDUAL.GENE_EXPRESSION$E.NA
  RESIDUAL.GENE_EXPRESSION$E.zero[is.na(RESIDUAL.GENE_EXPRESSION$E.NA)] = 0

@@

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  tmp.expr = RESIDUAL.GENE_EXPRESSION$E.zero
  tmp.expr = tmp.expr[apply(tmp.expr,1,var) !=0,]
  residualSigCovars = runPCAandPlotCorrelations(tmp.expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

### Sanity check
```{r residualSigCovars.manual, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION$E.zero, 
                                              COVARIATES, 
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)

residualSigCovars[["PC_res"]][[2]]$plotData
```
### Residual calculation
Calculate weighted residuals and add back "Dx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("Dx.Tissue", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION$E.NA = RESIDUAL.GENE_EXPRESSION$E.NA + 
  ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(RESIDUAL.GENE_EXPRESSION$E.zero))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION$E.zero, scale.=T, center = T)

@@

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION$E.zero)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

# Estimate voom weights
VOOM.WEIGHTS = voom(PROCESSED_COUNTS$filteredExprMatrix$counts, design=DESIGN$design, plot=F)
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E.NA
correlation <- parallelDuplicateCorrelation(VOOM.WEIGHTS, block = COVARIATES$Individual_ID)

@@

# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E.NA
FIT = lmFit(VOOM.WEIGHTS)

# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.TissueOther_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueOther_ACC",
                                     "Dx.TissueOther_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueOther_DLPFC"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts.NA %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$E.NA %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store residual gene expression for network analysis
RESIDUAL.GENE_EXPRESSION$E.NA %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_ACC_DLPFC_netResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for network analysis)', 
                parentId = CODE$properties$id)
annotations(nEXP_OBJ) = annotations(CODE)
annotations(nEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
nEXP_OBJ = synStore(nEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
